# Statistical Statistics {.tabset}

```{r sasOptions}
knitr::opts_chunk$set(cache = FALSE)

statReports<-"./statSummaries"
```

Note: all of the summaries below will have one fewer hour for the AQS sourced analysis. This is a bug, will try to resolve for next year.

## PM~2.5~

```{r pm25sas}

pm25sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% "PM25") %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% "PM25" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm25SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm25sas %<>% dplyr::mutate(ORIGIN="AQS")

```


```{r pm25sasECMS}
# get pm25 stations in data
pm25Stns<-data %>%
  dplyr::filter(PARAMETER=="PM25") %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(pm25Stns!=0)){

# import ecms sas from excel
pm25sasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "PM2.5_UNSUPPRESSED.xlsx")) %>%

# remove secondary header row
dplyr::slice(-1) %>%
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) %>%
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm25Stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm25sasECMS))
# utils::View(names(pm25sas))
# 
# tibble::tibble(names(pm25sasECMS),
#                names(pm25sas)) %>% utils::View(.)
# 
# pm25sasECMS %<>%
#   dplyr::select(1:31,33,34,32,everything())

names(pm25sasECMS) <- names(pm25sas)

}
 
```

```{r pm25sasDT}
if(length(pm25Stns)!=0){

  if(exists("pm25sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm25sasDT <- bind_rows(
  pm25sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  pm25sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm25sasDT,
    caption = dplyr::if_else(nrow(pm25sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")} # this seems redundant - TO DO: TRY REMOVING IT AND SEE IF IT CRASHES
  }

# case 2: no data for this parameter
if(length(pm25Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## PM~10~
```{r pm10sas}

pm10sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% "PM10") %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% "PM10" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm10SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm10sas %<>% dplyr::mutate(ORIGIN="AQS")

```


```{r pm10sasECMS}
# get pm10 stations in data
pm10Stns<-data %>%
  dplyr::filter(PARAMETER=="PM10") %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(pm10Stns!=0)){

# import ecms sas from excel
pm10sasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "PM10_UNSUPPRESSED.xlsx")) %>%

# remove secondary header row
dplyr::slice(-1) %>%
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) %>%
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm10Stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm10sasECMS))
# utils::View(names(pm10sas))
# utils::View(pm10sasECMS)
# 
# tibble::tibble(names(pm10sasECMS)[c(1:32,34,35,33,37:47,49:52)],
#                names(pm10sas)) %>% utils::View(.)

pm10sasECMS %<>%
  dplyr::select(1:32,34,35,33,everything())

names(pm10sasECMS) <- names(pm10sas)

}
 
```

```{r pm10sasDT}
if(length(pm10Stns)!=0){

  if(exists("pm10sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm10sasDT <- bind_rows(
  pm10sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  pm10sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm10sasDT,
    caption = dplyr::if_else(nrow(pm10sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(pm10Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## NO~2~

```{r no2sas}

no2sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("no2")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("no2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   no2SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
no2sas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r no2sasECMS}
# get no2 stations in data
no2Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("no2")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(no2Stns)!=0){

# import ecms sas from excel
no2sasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "NO2_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded column
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(no2Stns, "_", " "))


# tibble::tibble(names(no2sasECMS),
#                names(no2sas)) %>% View

names(no2sasECMS) <- names(no2sas)

}
 
```

```{r no2sasDT}
if(length(no2Stns)!=0){

  if(exists("no2sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

no2sasDT <- bind_rows(
  no2sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  no2sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    no2sasDT,
    caption = dplyr::if_else(nrow(no2sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(no2Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## NO

```{r noStats}

# data<-readr::read_rds("unverified_data.rds") %>%
#   dplyr::filter(STATION_NAME=="Castlegar Zinio Park" &
#            PARAMETER=="NO") %>% distinct()

noStats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("no")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("no") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   noStatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
noStats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r nosasECMS}
# get no stations in data
noStns<-data %>%
  dplyr::filter(PARAMETER==toupper("no")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(noStns)!=0){

# import ecms sas from excel
nosasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "NO_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(noStns, "_", " "))


# tibble::tibble(names(nosasECMS),
#                names(nosas)) %>% View

names(nosasECMS) <- names(nosas)

}
 
```

```{r nosasDT}
if(length(noStns)!=0){

  if(exists("nosasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

nosasDT <- bind_rows(
  nosasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  nosas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    nosasDT,
    caption = dplyr::if_else(nrow(nosasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(noStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## SO~2~

```{r so2sas}

so2sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("so2")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("so2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   so2SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

    # add column origin for where calculations originate from
so2sas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r so2sasECMS}
# get so2 stations in data
so2Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("so2")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(so2Stns)!=0){

# import ecms sas from excel
so2sasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "SO2_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(so2Stns, "_", " "))


# tibble::tibble(names(so2sasECMS),
#                names(so2sas)) %>% View

names(so2sasECMS) <- names(so2sas)
 
}
```

```{r so2sasDT}
if(length(so2Stns)!=0){

  if(exists("so2sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

so2sasDT <- bind_rows(
  so2sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  so2sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    so2sasDT,
    caption = dplyr::if_else(nrow(so2sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(so2Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## O~3~

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQS calculations, these 7 hours were not included which leads to small differences with the ECMS calculations.

```{r o3Stats}

 data<-readr::read_rds("unverified_data.rds") %>%
   dplyr::filter(STATION_NAME=="Castlegar Zinio Park" &
            PARAMETER=="O3") %>% distinct()

o3Stats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("o3")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("o3") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   o3StatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

 # add column origin for where calculations originate from
o3Stats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r o3sasECMS}
# get o3 stations in data
o3Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("o3")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(o3Stns!=0)){

# import ecms sas from excel
o3sasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "OZONE_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(o3Stns, "_", " "))


# tibble::tibble(names(o3sasECMS),
#                names(o3sas)) %>% View

names(o3sasECMS) <- names(o3sas)

}
 
```

```{r o3sasDT}
if(length(o3Stns)!=0){

  if(exists("o3sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

o3sasDT <- bind_rows(
  o3sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  o3sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    o3sasDT,
    caption = dplyr::if_else(nrow(o3sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(o3Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## H~2~S

```{r h2ssas}

h2ssas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("h2s") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   h2sSASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
h2ssas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r h2ssasECMS}
# get h2s stations in data
h2sStns<-data %>%
  dplyr::filter(PARAMETER==toupper("h2s")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(h2sStns)!=0){
# import ecms sas from excel
h2ssasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "H2S_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(h2sStns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(h2ssasECMS),
#                names(h2ssas)) %>% View

# utils::View(names(h2ssasECMS))

names(h2ssasECMS) <- names(h2ssas)

} 

```

```{r h2ssasDT}
if(length(h2sStns)!=0){

  if(exists("h2ssasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

h2ssasDT <- bind_rows(
  h2ssasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  h2ssas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    h2ssasDT,
    caption = dplyr::if_else(nrow(h2ssasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(h2sStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## TRS

```{r trssas}

trssas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("trs")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("trs") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   trsSASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

   # add column origin for where calculations originate from
trssas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r trssasECMS}
# get trs stations in data
trsStns<-data %>%
  dplyr::filter(PARAMETER==toupper("trs")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(trsStns!=0)){

# import ecms sas from excel
trssasECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "TRS_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(trsStns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(trssasECMS),
#                names(trssas)) %>% View

names(trssasECMS) <- names(trssas)

}
 
```

```{r trssasDT}
if(length(trsStns)!=0){

  if(exists("trssasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

trssasDT <- bind_rows(
  trssasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  trssas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    trssasDT,
    caption = dplyr::if_else(nrow(trssasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(trsStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## CO

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQS calculations, these 7 hours were not included which leads to small differences with the ECMS calculations.

```{r coStats}

coStats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("co")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("co") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   coStatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  
# add column origin for where calculations originate from
coStats %<>% 
  dplyr::mutate(ORIGIN="AQS",
                # round colunms that contain % in name to two digits
                dplyr::across(where(is.double),#dplyr::contains("%"),
                              ~round(.,digits=2)))

```

```{r coStatsECMS}
# get co stations in data
coStns<-data %>%
  dplyr::filter(PARAMETER==toupper("co")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(coStns)!=0){

# import ecms sas from excel
coStatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "CO_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columns
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(coStns, "_", " "))


# tibble::tibble(names(cosasECMS),
#                names(cosas)) %>% View

names(coStatsECMS) <- names(coStats)

}
 
```

```{r coStatsDT}
if(length(coStns)!=0){

  if(exists("coStatsECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

coStatsDT <- bind_rows(
  coStatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  coStats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    coStatsDT,
    caption = dplyr::if_else(nrow(coStatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No statistical summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(coStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

