# Statistics {.tabset}

```{r StatsOptions}
knitr::opts_chunk$set(cache = FALSE)

statReports<-"./statSummaries"
```

Note: all of the summaries below will have one fewer hour for the AQS-sourced analysis. 

## PM~2.5~

```{r pm25Stats}

pm25Stats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% "PM25") %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% "PM25" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm25StatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm25Stats %<>% dplyr::mutate(ORIGIN="AQS")

```


```{r pm25StatsECMS}
# get pm25 stations in data
pm25Stns<-data %>%
  dplyr::filter(PARAMETER=="PM25") %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(pm25Stns!=0)){

# import ecms Stats from excel
pm25StatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "PM25_UNSUPPRESSED.xlsx")) %>%

# remove secondary header row
dplyr::slice(-1) %>%
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) %>%
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm25Stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm25StatsECMS))
# utils::View(names(pm25Stats))
# 
# tibble::tibble(names(pm25StatsECMS),
#                names(pm25Stats)) %>% utils::View(.)
# 
# pm25StatsECMS %<>%
#   dplyr::select(1:31,33,34,32,everything())

names(pm25StatsECMS) <- names(pm25Stats)

}
 
```

```{r pm25StatsDT}
if(length(pm25Stns)!=0){

  if(exists("pm25StatsECMS") & nrow(pm25StatsECMS!=0)){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

    # GOT TO HERE - MERRITT NICOLA AVE MAML MISMATCH IN COLUMNS ECMS
    
pm25StatsDT <- bind_rows(
  pm25StatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)), #%>% utils::View(.),

  pm25Stats %>%
    dplyr::mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm25StatsDT,
    caption = dplyr::if_else(nrow(pm25StatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")} # this seems redundant - TO DO: TRY REMOVING IT AND SEE IF IT CRASHES
  }

# case 2: no data for this parameter
if(length(pm25Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## PM~10~
```{r pm10Stats}

pm10Stats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% "PM10") %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% "PM10" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm10StatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm10Stats %<>% dplyr::mutate(ORIGIN="AQS")

```


```{r pm10StatsECMS}
# get pm10 stations in data
pm10Stns<-data %>%
  dplyr::filter(PARAMETER=="PM10") %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(pm10Stns!=0)){

# import ecms Stats from excel
pm10StatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "PM10_UNSUPPRESSED.xlsx")) %>%

# remove secondary header row
dplyr::slice(-1) %>%
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) %>%
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm10Stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm10StatsECMS))
# utils::View(names(pm10Stats))
# utils::View(pm10StatsECMS)
# 
# tibble::tibble(names(pm10StatsECMS)[c(1:32,34,35,33,37:47,49:52)],
#                names(pm10Stats)) %>% utils::View(.)

pm10StatsECMS %<>%
  dplyr::select(1:32,34,35,33,everything())

names(pm10StatsECMS) <- names(pm10Stats)

}
 
```

```{r pm10StatsDT}
if(length(pm10Stns)!=0 ){

  if(exists("pm10StatsECMS") & nrow(pm10StatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm10StatsDT <- bind_rows(
  pm10StatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  pm10Stats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm10StatsDT,
    caption = dplyr::if_else(nrow(pm10StatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(pm10Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## NO~2~

```{r no2Stats}

no2Stats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("no2")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("no2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   no2StatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
no2Stats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r no2StatsECMS}
# get no2 stations in data
no2Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("no2")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(no2Stns)!=0){

# import ecms Stats from excel
no2StatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "NO2_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded column
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(no2Stns, "_", " "))


# tibble::tibble(names(no2StatsECMS),
#                names(no2Stats)) %>% View

names(no2StatsECMS) <- names(no2Stats)

}
 
```

```{r no2StatsDT}
if(length(no2Stns)!=0){

  if(exists("no2StatsECMS")& nrow(no2StatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

no2StatsDT <- dplyr::bind_rows(
  no2StatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  no2Stats %>%
    dplyr::mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    no2StatsDT,
    caption = dplyr::if_else(nrow(no2StatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(no2Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## NO

```{r noStats}

noStats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("no")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("no") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   noStatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
noStats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r noStatsECMS}
# get no stations in data
noStns<-data %>%
  dplyr::filter(PARAMETER==toupper("no")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(noStns)!=0){

# import ecms Stats from excel
noStatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "NO_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(noStns, "_", " "))


# tibble::tibble(names(noStatsECMS),
#                names(noStats)) %>% View

names(noStatsECMS) <- names(noStats)

}
 
```

```{r noStatsDT}
if(length(noStns)!=0){

  if(exists("noStatsECMS")& nrow(noStatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

noStatsDT <- bind_rows(
  noStatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  noStats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    noStatsDT,
    caption = dplyr::if_else(nrow(noStatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(noStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## SO~2~

```{r so2Stats}

so2Stats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("so2")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("so2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   so2StatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

    # add column origin for where calculations originate from
so2Stats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r so2StatsECMS}
# get so2 stations in data
so2Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("so2")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(so2Stns)!=0){

# import ecms Stats from excel
so2StatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "SO2_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(so2Stns, "_", " "))


# tibble::tibble(names(so2StatsECMS),
#                names(so2Stats)) %>% View

names(so2StatsECMS) <- names(so2Stats)
 
}
```

```{r so2StatsDT}
if(length(so2Stns)!=0){

  if(exists("so2StatsECMS")& nrow(so2StatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

so2StatsDT <- bind_rows(
  so2StatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  so2Stats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    so2StatsDT,
    caption = dplyr::if_else(nrow(so2StatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(so2Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## O~3~

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQS calculations, these 7 hours were not included which leads to small differences with the ECMS calculations.

```{r o3Stats}

o3Stats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("o3")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("o3") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   o3StatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

 # add column origin for where calculations originate from
o3Stats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r o3StatsECMS}
# get o3 stations in data
o3Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("o3")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(o3Stns!=0)){

# import ecms Stats from excel
o3StatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "OZONE_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(o3Stns, "_", " "))


# tibble::tibble(names(o3StatsECMS),
#                names(o3Stats)) %>% View

names(o3StatsECMS) <- names(o3Stats)

}
 
```

```{r o3StatsDT}
if(length(o3Stns)!=0){

  if(exists("o3StatsECMS")& nrow(o3StatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

o3StatsDT <- bind_rows(
  o3StatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  o3Stats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    o3StatsDT,
    caption = dplyr::if_else(nrow(o3StatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(o3Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## H~2~S

```{r h2sStats}

h2sStats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("h2s") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   h2sStatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
h2sStats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r h2sStatsECMS}
# get h2s stations in data
h2sStns<-data %>%
  dplyr::filter(PARAMETER==toupper("h2s")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(h2sStns)!=0){
# import ecms Stats from excel
h2sStatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "H2S_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(h2sStns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(h2sStatsECMS),
#                names(h2sStats)) %>% View

# utils::View(names(h2sStatsECMS))

names(h2sStatsECMS) <- names(h2sStats)

} 

```

```{r h2sStatsDT}
if(length(h2sStns)!=0){

  if(exists("h2sStatsECMS")& nrow(h2sStatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

h2sStatsDT <- bind_rows(
  h2sStatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  h2sStats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    h2sStatsDT,
    caption = dplyr::if_else(nrow(h2sStatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(h2sStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## TRS

```{r trsStats}

trsStats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("trs")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("trs") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   trsStatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

   # add column origin for where calculations originate from
trsStats %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r trsStatsECMS}
# get trs stations in data
trsStns<-data %>%
  dplyr::filter(PARAMETER==toupper("trs")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(trsStns!=0)){

# import ecms Stats from excel
trsStatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "TRS_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(trsStns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(trsStatsECMS),
#                names(trsStats)) %>% View

names(trsStatsECMS) <- names(trsStats)

}
 
```

```{r trsStatsDT}
if(length(trsStns)!=0){

  if(exists("trsStatsECMS")& nrow(trsStatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

trsStatsDT <- bind_rows(
  trsStatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  trsStats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    trsStatsDT,
    caption = dplyr::if_else(nrow(trsStatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(trsStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## CO

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQS calculations, these 7 hours were not included which leads to small differences with the ECMS calculations.

```{r coStats}

coStats<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("co")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("co") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   coStatsFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  
# add column origin for where calculations originate from
coStats %<>% 
  dplyr::mutate(ORIGIN="AQS",
                # round colunms that contain % in name to two digits
                dplyr::across(where(is.double),#dplyr::contains("%"),
                              ~round(.,digits=2)))

```

```{r coStatsECMS}
# get co stations in data
coStns<-data %>%
  dplyr::filter(PARAMETER==toupper("co")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(coStns)!=0){

# import ecms Stats from excel
coStatsECMS <- readxl::read_excel(
  file.path(statReports,                                            
            "CO_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columns
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(coStns, "_", " "))


# tibble::tibble(names(coStatsECMS),
#                names(coStats)) %>% View

names(coStatsECMS) <- names(coStats)

}
 
```

```{r coStatsDT}
if(length(coStns)!=0){

  if(exists("coStatsECMS")& nrow(coStatsECMS)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

coStatsDT <- bind_rows(
  coStatsECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  coStats %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    coStatsDT,
    caption = dplyr::if_else(nrow(coStatsECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No statistical summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(coStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

