# Wind Roses

Wind roses for `r params$year` and 5 previous years (when available). 

Things to look for when validating wind data:

+ Annual windrose
+ Windrose from previous years
+ Percent calm winds for the past 5-8 years
+ Do we have any pictures of the station?
+ Does the windrose make sense to you relative to the local topography?
+ RH - does RH get to 100% or does it max out at 97%? Has this changed recently?
+ Can I see any obvious breakpoints in a strip chart where something changes/

```{r windCache}
knitr::opts_chunk$set(cache = FALSE)
```


```{r windDataPrepQAQC}
# select wind data, get it in openair format

windData <- data %>% # data from importData chunk in index.Rmd
  
  dplyr::filter(PARAMETER %in% c("WSPD_SCLR", "WDIR_VECT")) %>%
  
  # contains X previous years as per _01.importData.html 
  dplyr::bind_rows(.,
                   prevYrWind) %>%
  
  # 2021 VALIDATION BUGS
  
  # # # COLWOOD CITY HALL 
  # duplicates in wspd_sclr,wdir_vect from 2020-01-01 03:00:00 to 2020-09-01 13:00:00 (one NA, one value)
  
  
  # # # PRINCE GEORGE EXPLORATION PLACE
  # duplicates in wspd_sclr,wdir_vect and humidity from 2021-01-01 01:00:00 until 2021-12-31 23:00:00
  
  # # # VANDERHOOF COURTHOUSE
  # duplicates in wspd_sclr,wdir_vect 2021-01-01 01:00:00 until 2021-12-31 23:00:00
  
  
  
  # # # 
  # duncan college street has duplicates for unique DATE_PST,STATION_NAME,PARAMETER
  # (no duplicates when grouped by STATION_NAME and STATION_NAME_FULL because _60 has
  # the duplicates i.e. UNSPECIFIED for instrument and "" for all the data). Filter out this data.
  # communicated to ecms
  
  dplyr::filter(!(STATION_NAME=="Duncan College Street" & INSTRUMENT == "UNSPECIFIED")) %>%
  
  # # # 
  # burns lake sheraton east - duplicates in wind data (one is prob from _60 but should still get cleaned up). 
  # NOT communicated to ecms
  
  dplyr::filter(!(STATION_NAME=="Burns Lake Sheraton East" & 
                    INSTRUMENT == "WIND DIR VECTOR" &
                    lubridate::year(DATE_PST)==2016)) %>%

  # # # 
  # courtenay elementary school - duplicates from 2017-01-01 until 2019-12-31 where instrument=WIND DIR VECTOR are all NA's and INSTRUMENT=WIND DIR have values


  # remove wind direction duplicates (all NA values)
  dplyr::filter(!(STATION_NAME=="Courtenay Elementary School" &
                  INSTRUMENT=="WIND DIR VECTOR" &
                  lubridate::year(DATE_PST) %in% 2017:2019))  %>%

  # # # FRASER LAKE ENDAKO MINES
  dplyr::filter(!(STATION_NAME=="Fraser Lake Endako Mines" &
                  INSTRUMENT=="UNSPECIFIED" &
                  lubridate::year(DATE_PST)==2016)) %>%

  # # # TAYLOR SOUTH HILL
  # nuanced duplicates in wspd_sclr and wdir_vect for all of 2020. 
  # For jan 1, 2020 00:00:00 INSTRUMENT %in% c("WIND DIR VECTOR", "WIND SPEED") need to removed
  # for the rest of the year INSTRUMENT == "UNSPECIFIED" needs to be removed
  dplyr::filter(!(STATION_NAME=="Taylor South Hill" &
                  INSTRUMENT %in% c("WIND DIR VECTOR",
                                    "WIND SPEED") &
                  DATE_PST==lubridate::ymd_hms("2020-01-01 00:00::00",
                                               tz="Etc/GMT+8"))) %>%
  
  dplyr::filter(!(STATION_NAME=="Taylor South Hill" &
                  INSTRUMENT == "UNSPECIFIED" &
                  DATE_PST %in% seq(lubridate::ymd_hms("2020-01-01 01:00::00",
                                               tz="Etc/GMT+8"),
                                    lubridate::ymd_hms("2020-12-31 23:00::00",
                                               tz="Etc/GMT+8"),
                                    by="hour"
                                    )))

  
# # # COURTENAY ELEMENTARY SCHOOL WIND SPEED
# couldn't figure out how to add this to the pipe above (ideal option)
  # wind speed has duplicates with double hours with two numeric values (one is zero and on is the real value) between 2017-05-29 20:00:00 and 2017-06-01 00:00:00 (inclusive) - THIS WILL NEED TO BE REMOVED ONCE FIXED ON THE FTP OTHERWISE IT'S GOING TO DELETE REAL DATA

# if(
#   
#   stringr::str_detect(params$preppedData,
#                       "Courtenay Elementary School")
# ){windData<-
#   
#   dplyr::anti_join(
#     windData,
#     #isolate even rows to remove
#     windData %>%
#       dplyr::filter(
#         STATION_NAME == "Courtenay Elementary School",
#         PARAMETER == "WSPD_SCLR" &
#           DATE_PST %in% seq(
#             lubridate::ymd_hms("2017-05-29 20:00:00",
#                                tz = "Etc/GMT+8"),
#             lubridate::ymd_hms("2017-06-01 00:00:00",
#                                tz = "Etc/GMT+8"),
#             by = "hour"
#           )
#       ) %>%
#       # even rows - shoudl be all zeros
#       dplyr::slice(seq(2,nrow(.),2))
#       )}
# 
# ## # # FIND DUPLICATES
#  duplicates<-windData %>%
#     dplyr::group_by(DATE_PST, STATION_NAME, PARAMETER) %>%
#     dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
#     dplyr::filter(n > 1L) %>%
#    dplyr::left_join(.,
#                     windData,
#                     by=c("DATE_PST","STATION_NAME","PARAMETER"))
# 
#  write.csv(duplicates,"duplicates.csv")
# 
#  duplicates %>%
#    dplyr::group_by(PARAMETER) %>%
#    dplyr::slice(1:6) %>% utils::View()
# 
#   # are any groups all NA's? makes it easy to remove
#  duplicates %>%
#    # dplyr::filter(PARAMETER=="WSPD_SCLR") %>%
#    dplyr::group_by(PARAMETER,INSTRUMENT) %>%
#    dplyr::summarise(`# NA's`=sum(is.na(RAW_VALUE)),
#                     `# Obs`=sum(!is.na(RAW_VALUE)),
#                     `# Hours`=dplyr::n())
# 
# 
# 
# duplicates %>%
#   dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) %>%
#   dplyr::summarise(start=min(DATE_PST),
#                    end=max(DATE_PST))


 
 # # # END DUPLICATES
  
```

```{r windDataOpenAir}
if( all(nrow(windData)!=0, # at least one row of data
        any(unique(windData$PARAMETER) %in% "WSPD_SCLR"),
        any(unique(windData$PARAMETER) %in% "WDIR_VECT")
    )
  ){
  
 
  windData %<>%
    
    dplyr::select(date = DATE_PST,
                  STATION_NAME,
                  # INSTRUMENT,
                  PARAMETER,
                  RAW_VALUE) %>%
    
    tidyr::pivot_wider(.,
                       names_from = PARAMETER,
                       values_from = RAW_VALUE) %>%
    
    dplyr::rename(ws = WSPD_SCLR,
                  wd = WDIR_VECT) %>%
    
    dplyr::mutate(ws = ifelse(is.na(wd), NA_real_, ws),
                  wd = ifelse(is.na(ws), NA_real_, wd))
}

  

```

```{r windRose}
if(all(
  # at least a row of data
  nrow(windData) != 0, 
  # some data in the year being validated
  length(unique(lubridate::year(windData$date)) %in% params$year)!=0,
  # a column called ws
  any(names(windData) %in% "ws"),
  # a column called wd
  any(names(windData) %in% "wd")
         
       )
) {
  

purrr::walk(unique(lubridate::year(windData$date)) %>% sort,
    
    function(year){
      
      # TESTING
      
      # year<-2020
      # 
      # windDataBackup<-windData
      # 
      # windData<-windDataBackup
      
      # END TESTING
      
      station<-unique(windData$STATION_NAME)
      
      windData %<>%
        dplyr::filter(lubridate::year(date) %in% year)
      
      #number of calm hours
      ncalm <- windData %>%
        dplyr::filter(ws < 0.5) %>%
        dplyr::summarise(calms = n())
      
      #total number of valid ws hours
      ntotal <- windData %>%
        dplyr::filter(!is.na(ws)) %>%
        dplyr::summarise(total = n())
      
      #percentage calm (ws<0.5 m/s)
      pcalm <- round(100 * ncalm / ntotal,
                     digits = 2)
      
      #filter out calm windData
      roseData <- windData %>%
        dplyr::filter(ws >= 0.5)
      
      if(nrow(windData)==sum(is.na(windData$ws)) | nrow(roseData)==0){
        
        paste("There is either no paired wind data at",
              station,
              "or there is no paired wind data above the 0.5 m/s threshold.")
        
      } else {
      
      
      
      #windRose
      windRose(
        roseData,
        annotate = FALSE,
        breaks = c(0.5, 1.5, 3.3, 5.5, 7.9, 10.7, 13.8, 17.1),
        #Beaufort scale with 0.5 as lowest cut point.
        sub = paste("Calms (=<0.5m/s)=", pcalm, "%"),
        key.position = "right",
        main = stringr::str_c(year," Wind Rose at ",station),
        angle = 360 / 16,
        #16 spokes
        cols = "jet",
        paddle = FALSE
      ) 
      
      } # end else
      
    } #end function(station)
    
    ) # map
  
} else{
  
  htmltools::tags$p("This station either doesn't measure wind, has no wind data for the year being validated, or it is missing one of WSPD_SCLR or WDIR_VECT")
  
}


```
