# Wind Roses

Wind roses for `r params$year` and 5 previous years (when available). 

Things to look for when validating wind data:

+ Annual windrose
+ Windrose from previous years
+ Percent calm winds for the past 5-8 years
+ Do we have any pictures of the station?
+ Does the windrose make sense to you relative to the local topography?
+ RH - does RH get to 100% or does it max out at 97%? Has this changed recently?
+ Can I see any obvious breakpoints in a strip chart where something changes/

```{r windCache}
knitr::opts_chunk$set(cache = FALSE)
```


```{r windDataPrepQAQC}
# select wind data, get it in openair format

windData <- data %>% # data from importData chunk in index.Rmd
  
  dplyr::filter(PARAMETER %in% c("WSPD_SCLR", "WDIR_VECT")) %>%
  
  # contains X previous years as per _01.importData.html 
  dplyr::bind_rows(.,
                   prevYrWind)


```

```{r duplicates,eval=FALSE,include=FALSE}
# # # # # FIND DUPLICATES
 duplicates<-windData %>%
    dplyr::group_by(DATE_PST, STATION_NAME, PARAMETER) %>%
    dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
    dplyr::filter(n > 1L) %>%
   dplyr::left_join(.,
                    windData,
                    by=c("DATE_PST","STATION_NAME","PARAMETER"))

utils::View(duplicates)

# save duplicates as csv
 write.csv(duplicates,"duplicates.csv")

 
 # # # EXPLORATORY DATA ANALYSIS # # #
 
 #look at the first 6 rows of each set of duplicates (by PARAMETER)
 duplicates %>%
   dplyr::group_by(PARAMETER) %>%
   dplyr::slice(1:6) %>% utils::View()

  # are any groups all NA's? makes it easy to remove
 duplicates %>%
   # dplyr::filter(PARAMETER=="WSPD_SCLR") %>%
   dplyr::group_by(PARAMETER,INSTRUMENT) %>%
   dplyr::summarise(`# NA's`=sum(is.na(RAW_VALUE)),
                    `# Obs`=sum(!is.na(RAW_VALUE)),
                    `# Hours`=dplyr::n())


# when did the duplicates start and end?
duplicates %>%
  dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) %>%
  dplyr::summarise(start=min(DATE_PST),
                   end=max(DATE_PST))

# to look at the whole data set (sorted by PARAMETER and DATE_PST)
duplicates %>%
  dplyr::arrange(PARAMETER,DATE_PST) %>% utils::View()


 
duplicates %>%
  dplyr::filter(PARAMETER=="WDIR_VECT") %>% utils::View()
 # odd rows - shoudl be all NA's
      dplyr::slice(seq(1,nrow(.),2)) %>% utils::View()

# preview windData
windData %>%
  dplyr::filter(INSTRUMENT=="UNSPECIFIED" &
                  lubridate::year(DATE_PST)==2021) %>% utils::View()
 
 # # # END DUPLICATES
  
```

```{r windDataOpenAir}
if( all(nrow(windData)!=0, # at least one row of data
        any(unique(windData$PARAMETER) %in% "WSPD_SCLR"),
        any(unique(windData$PARAMETER) %in% "WDIR_VECT")
    )
  ){
  
 
  windData %<>%
    
    dplyr::select(date = DATE_PST,
                  STATION_NAME,
                  # INSTRUMENT,
                  PARAMETER,
                  RAW_VALUE) %>%
    
    tidyr::pivot_wider(.,
                       names_from = PARAMETER,
                       values_from = RAW_VALUE) %>%
    
    dplyr::rename(ws = WSPD_SCLR,
                  wd = WDIR_VECT) %>%
    
    dplyr::mutate(ws = ifelse(is.na(wd), NA_real_, ws),
                  wd = ifelse(is.na(ws), NA_real_, wd))
}

  

```

```{r windRose}
if(all(
  # at least a row of data
  nrow(windData) != 0, 
  # some data in the year being validated
  length(unique(lubridate::year(windData$date)) %in% params$year)!=0,
  # a column called ws
  any(names(windData) %in% "ws"),
  # a column called wd
  any(names(windData) %in% "wd")
         
       )
) {
  

purrr::walk(unique(lubridate::year(windData$date)) %>% sort,
    
    function(year){
      
      # TESTING
      
      # year<-2020
      # 
      # windDataBackup<-windData
      # 
      # windData<-windDataBackup
      
      # END TESTING
      
      station<-unique(windData$STATION_NAME)
      
      windData %<>%
        dplyr::filter(lubridate::year(date) %in% year)
      
      #number of calm hours
      ncalm <- windData %>%
        dplyr::filter(ws < 0.5) %>%
        dplyr::summarise(calms = n())
      
      #total number of valid ws hours
      ntotal <- windData %>%
        dplyr::filter(!is.na(ws)) %>%
        dplyr::summarise(total = n())
      
      #percentage calm (ws<0.5 m/s)
      pcalm <- round(100 * ncalm / ntotal,
                     digits = 2)
      
      #filter out calm windData
      roseData <- windData %>%
        dplyr::filter(ws >= 0.5)
      
      if(nrow(windData)==sum(is.na(windData$ws)) | nrow(roseData)==0){
        
        paste("There is either no paired wind data at",
              station,
              "or there is no paired wind data above the 0.5 m/s threshold.")
        
      } else {
      
      
      
      #windRose
      windRose(
        roseData,
        annotate = FALSE,
        breaks = c(0.5, 1.5, 3.3, 5.5, 7.9, 10.7, 13.8, 17.1),
        #Beaufort scale with 0.5 as lowest cut point.
        sub = paste("Calms (=<0.5m/s)=", pcalm, "%"),
        key.position = "right",
        main = stringr::str_c(year," Wind Rose at ",station),
        angle = 360 / 16,
        #16 spokes
        cols = "jet",
        paddle = FALSE
      ) 
      
      } # end else
      
    } #end function(station)
    
    ) # map
  
} else{
  
  htmltools::tags$p("This station either doesn't measure wind, has no wind data for the year being validated, or it is missing one of WSPD_SCLR or WDIR_VECT")
  
}


```
