# Wind Roses

Wind roses for `r params$year` and 5 previous years (when available). 

Things to look for when validating wind data:

+ Annual windrose
+ Windrose from previous years
+ Percent calm winds for the past 5-8 years
+ Do we have any pictures of the station?
+ Does the windrose make sense to you relative to the local topography?
+ RH - does RH get to 100% or does it max out at 97%? Has this changed recently?
+ Can I see any obvious breakpoints in a strip chart where something changes/

```{r wind-cache}
knitr::opts_chunk$set(cache = FALSE)
```


```{r wind-data-prep-qaqc}
# select wind data, get it in openair format

wind_data <- # contains X previous years as per _01.import-data.html
  dplyr::bind_rows(
    data |> # data from import-data chunk in index.Rmd
      
      dplyr::filter(PARAMETER %in% c("WSPD_SCLR", "WDIR_VECT")),
    prev_yrs_wind
  )
```

```{r duplicates,eval=FALSE,include=FALSE}
# # # # # FIND DUPLICATES
 duplicates<-wind_data |>
    dplyr::group_by(DATE_PST, STATION_NAME, PARAMETER) |>
    dplyr::summarise(n = dplyr::n(), .groups = "drop") |>
    dplyr::filter(n > 1L) |>
   dplyr::left_join(x=_,
                    wind_data,
                    by=c("DATE_PST","STATION_NAME","PARAMETER"))

utils::View(duplicates)

# save duplicates as csv
 write.csv(duplicates,"duplicates.csv")

 
 # # # EXPLORATORY DATA ANALYSIS # # #
 
 #look at the first 6 rows of each set of duplicates (by PARAMETER)
 duplicates |>
   dplyr::group_by(PARAMETER) |>
   dplyr::slice(1:6) |> utils::View()

  # are any groups all NA's? makes it easy to remove
 duplicates |>
   # dplyr::filter(PARAMETER=="WSPD_SCLR") |>
   dplyr::group_by(PARAMETER,INSTRUMENT) |>
   dplyr::summarise(`# NA's`=sum(is.na(RAW_VALUE)),
                    `# Obs`=sum(!is.na(RAW_VALUE)),
                    `# Hours`=dplyr::n())


# when did the duplicates start and end?
duplicates |>
  dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) |>
  dplyr::summarise(start=min(DATE_PST),
                   end=max(DATE_PST))

# to look at the whole data set (sorted by PARAMETER and DATE_PST)
duplicates |>
  dplyr::arrange(PARAMETER,DATE_PST) |> utils::View()


 
duplicates |>
  dplyr::filter(PARAMETER=="WDIR_VECT") |> utils::View()
 # odd rows - shoudl be all NA's
      dplyr::slice(seq(1,nrow(.),2)) |> utils::View()

# preview wind_data
wind_data |>
  dplyr::filter(INSTRUMENT=="UNSPECIFIED" &
                  lubridate::year(DATE_PST)==2021) |> utils::View()
 
 # # # END DUPLICATES
  
```

```{r wind-data-openair}
if( all(nrow(wind_data)!=0, # at least one row of data
        any(unique(wind_data$PARAMETER) %in% "WSPD_SCLR"),
        any(unique(wind_data$PARAMETER) %in% "WDIR_VECT")
    )
  ){
  
  wind_data <- wind_data |>
    
    dplyr::select(date = DATE_PST,
                  STATION_NAME,
                  # INSTRUMENT,
                  PARAMETER,
                  RAW_VALUE) |>
    
    tidyr::pivot_wider(data=_,
                       names_from = PARAMETER,
                       values_from = RAW_VALUE) |>
    
    dplyr::rename(ws = WSPD_SCLR,
                  wd = WDIR_VECT) |>
    
    dplyr::mutate(ws = ifelse(is.na(wd), NA_real_, ws),
                  wd = ifelse(is.na(ws), NA_real_, wd))
}


# openair::summaryPlot(wind_data)
```

```{r wind-rose, fig.show='hide'}
if(all(
  # at least a row of data
  nrow(wind_data) != 0, 
  # some data in the year being validated
  length(unique(lubridate::year(wind_data$date)) %in% params$year)!=0,
  # a column called ws
  any(names(wind_data) %in% "ws"),
  # a column called wd
  any(names(wind_data) %in% "wd")
         
       )
) {
 
  
  station<-unique(wind_data$STATION_NAME)

   
plot_list<-lapply(unique(lubridate::year(wind_data$date)) |> sort(x=_),
                  
# plot_list<-purrr::walk(unique(lubridate::year(wind_data$date)) |> sort(x=_),
    
    function(year){
      
      # TESTING
      
      # year<-2024
      # 
      # wind_dataBackup<-wind_data
      # 
      # wind_data<-wind_dataBackup
      
      # END TESTING
      
      
      wind_data %<>%
        dplyr::filter(lubridate::year(date) %in% year)
      
      #number of calm hours
      ncalm <- wind_data |>
        dplyr::filter(ws < 0.5) |>
        dplyr::summarise(calms = n())
      
      #total number of valid ws hours
      ntotal <- wind_data |>
        dplyr::filter(!is.na(ws)) |>
        dplyr::summarise(total = n())
      
      #percentage calm (ws<0.5 m/s)
      pcalm <- round(100 * ncalm / ntotal,
                     digits = 2)
      
      #filter out calm wind_data
      roseData <- wind_data |>
        dplyr::filter(ws >= 0.5)
      
      if(nrow(wind_data)==sum(is.na(wind_data$ws)) | nrow(roseData)==0){
        
        #make an empty plot when there is no data for a year
        ggplot2::ggplot(data=tibble::tibble(
          y=NA_real_,
          x=NA_real_),
          ggplot2::aes(x=x,y=y
        ))+
          ggplot2::annotate("text",x=0,y=0,label="There is no valid paired wind data for this year.")+
          ggplot2::labs(x="",
                        y="",
                        title=year)+
          ggplot2::theme_bw()+
          ggplot2::theme(axis.text.x = ggplot2::element_blank(), 
                axis.ticks.x = ggplot2::element_blank(), 
                axis.text.y = ggplot2::element_blank(), 
                axis.ticks.y = ggplot2::element_blank()) +
          ggplot2::coord_polar()
        
        
      } else {
      
      
      
      #windRose
      p<-windRose(
        roseData,
        annotate = FALSE,
        breaks = c(0.5, 1.5, 3.3, 5.5, 7.9, 10.7, 13.8, 17.1),
        #Beaufort scale with 0.5 as lowest cut point.
        sub = paste("Calms (=<0.5m/s)=", pcalm, "%"),
        key.position = "right",
        main = stringr::str_c(year),
        angle = 360 / 16,
        #16 spokes
        cols = "jet",
        paddle = FALSE
      ) 
      
      p$plot
      
      } # end else
 
    } #end function(station)
     ) # map
 
} else{
  
  plot_list<-htmltools::tags$p("This station either doesn't measure wind, has no wind data for the year being validated, or it is missing one of WSPD_SCLR or WDIR_VECT")
  
}


```

```{r wind-rose-fig-dims}
#define width and height of wind rose figures based on length of plot_list

fig_height<-dplyr::case_when(
  length(plot_list) %in% 1:2 ~ 4,
  length(plot_list) %in% 3:4 ~ 8,
  length(plot_list) %in% 5:6 ~ 12,
  length(plot_list) %in% 7:8 ~ 16
  
)

```



```{r wind-rose-output,fig.height=fig_height}
if(is.null(plot_list$name)){
  gridExtra::grid.arrange(grobs=plot_list,
                        ncol=dplyr::if_else(length(plot_list)==1,1,2),
                        top=unique(wind_data$STATION_NAME))
}else{
  plot_list 
}
```

