# Statistics {.tabset}

```{r StatsOptions}
knitr::opts_chunk$set(cache = FALSE)

stat_reports<-"./stat-summaries"
```

Note: all of the summaries below will have one fewer hour for the AQAS-sourced analysis. 

## PM~2.5~

```{r pm25_stats}

pm25_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% "PM25") |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               #testing
               # station<-"Agassiz Centennial Park"
               
               station<-data |>
                 dplyr::filter(PARAMETER %in% "PM25" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                  # testing
                  # instrument<-"PM25_SHARP5030i"
                              
                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm25_stats_fcn(data=instrument,
                                  year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm25_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```


```{r pm25_stats_aqm}
# get pm25 stations in data
pm25_stns<-data |>
  dplyr::filter(PARAMETER=="PM25") |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(pm25_stns!=0)){

# import aqm Stats from excel
pm25_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("PM25_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>

# remove secondary header row
dplyr::slice(-1) |>
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) |>
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm25_stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm25_stats_aqm))
# utils::View(names(pm25_stats))
# 
# tibble::tibble(names(pm25_stats_aqm),
#                names(pm25_stats)) |> utils::View(.)
# 
# pm25_stats_aqm %<>%
#   dplyr::select(1:31,33,34,32,everything())

names(pm25_stats_aqm) <- names(pm25_stats)

}
 
```

```{r pm25_stats_dt}
if(length(pm25_stns)!=0){

  if(exists("pm25_stats_aqm") & nrow(pm25_stats_aqm!=0)){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm25_stats_dt <- bind_rows(
  pm25_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)), #|> utils::View(.),

  pm25_stats |>
    dplyr::mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm25_stats_dt,
    caption = dplyr::if_else(nrow(pm25_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to aqm stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from aqm.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")} # this seems redundant - TO DO: TRY REMOVING IT AND SEE IF IT CRASHES
  }

# case 2: no data for this parameter
if(length(pm25_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## PM~10~
```{r pm10_stats}

pm10_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% "PM10") |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% "PM10" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm10_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm10_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```


```{r pm10_stats_aqm}
# get pm10 stations in data
pm10_stns<-data |>
  dplyr::filter(PARAMETER=="PM10") |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(pm10_stns!=0)){

# import _aqm Stats from excel
pm10_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("PM10_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>

# remove secondary header row
dplyr::slice(-1) |>
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) |>
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm10_stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm10_stats_aqm))
# utils::View(names(pm10_stats))
# utils::View(pm10_stats_aqm)
# 
# tibble::tibble(names(pm10_stats_aqm)[c(1:32,34,35,33,37:47,49:52)],
#                names(pm10_stats)) |> utils::View(.)

pm10_stats_aqm %<>%
  dplyr::select(1:32,34,35,33,everything())

names(pm10_stats_aqm) <- names(pm10_stats)

}
 
```


```{r pm10_stats_dt}
if(length(pm10_stns)!=0 ){

  if(exists("pm10_stats_aqm") & nrow(pm10_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm10_stats_dt <- bind_rows(
  pm10_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  pm10_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm10_stats_dt,
    caption = dplyr::if_else(nrow(pm10_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(pm10_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## NO~2~

```{r no2_stats}

no2_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("no2")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("no2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   no2_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
no2_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```

```{r no2_stats_aqm}
# get no2 stations in data
no2_stns<-data |>
  dplyr::filter(PARAMETER==toupper("no2")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(no2_stns)!=0){

# import _aqm Stats from excel
no2_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("NO2_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>
  
  # remove unneeded column
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(no2_stns, "_", " "))


# tibble::tibble(names(no2_stats_aqm),
#                names(no2_stats)) |> View

names(no2_stats_aqm) <- names(no2_stats)

}
 
```

```{r no2_stats_dt}
if(length(no2_stns)!=0){

  if(exists("no2_stats_aqm")& nrow(no2_stats_aqm)!=0){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

no2_stats_dt <- dplyr::bind_rows(
  no2_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  no2_stats |>
    dplyr::mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    no2_stats_dt,
    caption = dplyr::if_else(nrow(no2_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(no2_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## NO

```{r no_stats}

no_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("no")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,


             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("no") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   no_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
no_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```

```{r no_stats_aqm}
# get no stations in data
no_stns<-data |>
  dplyr::filter(PARAMETER==toupper("no")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(no_stns)!=0){

# import _aqm Stats from excel
no_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("NO_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(no_stns, "_", " "))


# tibble::tibble(names(no_stats_aqm),
#                names(no_stats)) |> View

names(no_stats_aqm) <- names(no_stats)

}
 
```

```{r no_stats_dt}
if(length(no_stns)!=0){


  if(exists("no_stats_aqm")& nrow(no_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

no_stats_dt <- bind_rows(
  no_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  no_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    no_stats_dt,
    caption = dplyr::if_else(nrow(no_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(no_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## SO~2~

```{r so2_stats}

so2_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("so2")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("so2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   so2_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

    # add column origin for where calculations originate from
so2_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```

```{r so2_stats_aqm}
# get so2 stations in data
so2_stns<-data |>
  dplyr::filter(PARAMETER==toupper("so2")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(so2_stns)!=0){

# import _aqm Stats from excel
so2_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("SO2_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(so2_stns, "_", " "))


# tibble::tibble(names(so2_stats_aqm),
#                names(so2_stats)) |> View

names(so2_stats_aqm) <- names(so2_stats)
 
}
```

```{r so2_stats_dt}
if(length(so2_stns)!=0){

  if(exists("so2_stats_aqm")& nrow(so2_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

so2_stats_dt <- bind_rows(
  so2_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  so2_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    so2_stats_dt,
    caption = dplyr::if_else(nrow(so2_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(so2_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## O~3~

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQAS calculations, these 7 hours were not included which leads to small differences with the AQM calculations.

```{r o3_stats}

o3_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("o3")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("o3") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   o3_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

 # add column origin for where calculations originate from
o3_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```

```{r o3_stats_aqm}
# get o3 stations in data
o3_stns<-data |>
  dplyr::filter(PARAMETER==toupper("o3")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(o3_stns!=0)){

# import _aqm Stats from excel
o3_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("OZONE_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(o3_stns, "_", " "))


# tibble::tibble(names(o3_stats_aqm),
#                names(o3_stats)) |> View

names(o3_stats_aqm) <- names(o3_stats)

}
 
```

```{r o3_stats_dt}
if(length(o3_stns)!=0){

  if(exists("o3_stats_aqm")& nrow(o3_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

o3_stats_dt <- bind_rows(
  o3_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  o3_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    o3_stats_dt,
    caption = dplyr::if_else(nrow(o3_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(o3_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## H~2~S

```{r h2s_stats}

h2s_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("h2s")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("h2s") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   h2s_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
h2s_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```

```{r h2s_stats_aqm}
# get h2s stations in data
h2s_stns<-data |>
  dplyr::filter(PARAMETER==toupper("h2s")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(h2s_stns)!=0){
# import _aqm Stats from excel
h2s_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("H2S_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(h2s_stns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(h2s_stats_aqm),
#                names(h2s_stats)) |> View

# utils::View(names(h2s_stats_aqm))

names(h2s_stats_aqm) <- names(h2s_stats)

} 

```

```{r h2s_stats_dt}
if(length(h2s_stns)!=0){

  if(exists("h2s_stats_aqm")& nrow(h2s_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

h2s_stats_dt <- bind_rows(
  h2s_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  h2s_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    h2s_stats_dt,
    caption = dplyr::if_else(nrow(h2s_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(h2s_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## TRS

```{r trs_stats}

trs_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("trs")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("trs") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   trs_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

   # add column origin for where calculations originate from
trs_stats %<>% dplyr::mutate(ORIGIN="AQAS")

```

```{r trs_stats_aqm}
# get trs stations in data
trs_stns<-data |>
  dplyr::filter(PARAMETER==toupper("trs")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(trs_stns!=0)){

# import _aqm Stats from excel
trs_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("TRS_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))) |>
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(trs_stns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(trs_stats_aqm),
#                names(trs_stats)) |> View

names(trs_stats_aqm) <- names(trs_stats)

}
 
```

```{r trs_stats_dt}
if(length(trs_stns)!=0){

  if(exists("trs_stats_aqm")& nrow(trs_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

trs_stats_dt <- bind_rows(
  trs_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  trs_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    trs_stats_dt,
    caption = dplyr::if_else(nrow(trs_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No Stats summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(trs_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## CO

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQAS calculations, these 7 hours were not included which leads to small differences with the AQM calculations.

```{r co_stats}

co_stats<-purrr::map_dfr((data |>
                dplyr::filter(PARAMETER %in% toupper("co")) |>
                dplyr::distinct(STATION_NAME) |>
                dplyr::arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data |>
                 dplyr::filter(PARAMETER %in% toupper("co") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station |>
                     dplyr::filter(INSTRUMENT %in% instrument)

                   co_stats_fcn(data=instrument,year=params$year)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  
# add column origin for where calculations originate from
co_stats %<>% 
  dplyr::mutate(ORIGIN="AQAS",
                # round colunms that contain % in name to two digits
                dplyr::across(where(is.double),#dplyr::contains("%"),
                              ~round(.,digits=2)))

```

```{r co_stats_aqm}
# get co stations in data
co_stns<-data |>
  dplyr::filter(PARAMETER==toupper("co")) |>
  dplyr::pull(STATION_NAME) |>
  unique(x=_)

if(length(co_stns)!=0){

# import _aqm Stats from excel
co_stats_aqm <- readxl::read_excel(
  file.path(stat_reports,                                            
            stringr::str_c("CO_stats_",
                           params$year,
                           ".xlsx",
                           sep=""))
  ) |>
  
  # remove unneeded columns
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) |> 

# remove secondary header row
dplyr::slice(-1) |>

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "AQM") |>
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(co_stns, "_", " "))


# tibble::tibble(names(co_stats_aqm),
#                names(co_stats)) |> View

names(co_stats_aqm) <- names(co_stats)

}
 
```

```{r co_stats_dt}
if(length(co_stns)!=0){

  if(exists("co_stats_aqm")& nrow(co_stats_aqm)!=0){

    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

co_stats_dt <- bind_rows(
  co_stats_aqm |>
    dplyr::mutate_all(as.character) |>
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  co_stats |>
    mutate_all(as.character)

) |>
  dplyr::arrange(`STATION NAME`) |>
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    co_stats_dt,
    caption = dplyr::if_else(nrow(co_stats_aqm)!=0,
                             "AQM and AQAS calculated statistics.There will be one fewer valid hour compared to AQM stats, I'll try to resolve this for next year.",
                             "AQAS calculated statistics. (No summary available from AQM.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No statistical summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(co_stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

