---
title: "Import and Prep Data"
output: html_notebook
---

Must have local mirrored copy of ftp site in .feather format. (www.github.com/DonnaHaga/dataImport)

```{r setup}
library(tidyverse)
# source from github:
#https://github.com/opetchey/RREEBES/wiki/Reading-data-and-code-from-an-online-github-repository

# source importFeatherFcn from github:
source("../dataImport/functions/importFeatherFcn.R")

# devtools::source_url("https://raw.githubusercontent.com/DonnaHaga/dataImport/master/functions/importFeatherFcn.R")

```

Specify the paths to the local FTP duplicate (.feather); type of data (time period and unverified or verified) is also specified here.

```{r pathsToData}
# Path to feather data: 

airFTP<-"C:/airFTPdata"

# path to unverified data
(dataPath<-file.path(airFTP,
                    "Hourly_Raw_Air_Data/Year_to_Date"))
```

```{r declareParameters}

# FILTER FOR YEAR TO VALIDATE:
yearToValidate<-2021

# Import feather data for all parameters and combine into one tibble,
# filter for yearToValidate

# list all files in dataPath:
 # dir(dataPath)

parameters<-c("CO",
              "H2S",
              "HF",
              "HUMIDITY",
              "NO",
              "NO2",
              "NOX",
              "O3",
              "PM10",
              "PM25",
              "SO2",
              "TEMP_MEAN",
              "TRS",
              "WDIR_VECT",
              "WSPD_SCLR")


# generate allStations = character vector of all stations:
allStations <- feather::read_feather(file.path(dataPath,
                                               "bc_air_monitoring_stations.feather")) %>%
  dplyr::pull(STATION_NAME) %>% unique
```

```{r importData}
# call the importFeatherFcn to import data into R.
system.time({
data<-purrr::map_dfr(parameters,
                     
                     function(x){
                       
                       paste("Importing",x,"data...")
                       
                       importFeatherFcn(folder=dataPath,
                                        parameter = x,
                                        station="all")
                                        
                     })  %>%# map_dfr
  # filter for yearToValidate:
  dplyr::filter(format(DATE_PST,"%Y") %in% yearToValidate)

})

# GOT TO HERE
# saveRDS(data,"2021data.rds")

# import previous year's wind data for comparison
prevYrWind<-purrr::map_dfr(c("WSPD_SCLR","WDIR_VECT"),
                     
                     function(x){
                       
                       paste("Importing",x,"data...")
                       
                       importFeatherFcn(
                         # path to unverified data
                         folder=file.path(airFTP,
                                           "AnnualSummary",
                                           yearToValidate-1),
                                        parameter = x,
                                        station="all")
                       
                     })  %>%# map_dfr
  # filter for yearToValidate-1:
  dplyr::filter(format(DATE_PST,"%Y") %in% (yearToValidate-1))


# bind the two data sets together, call it data
data<-dplyr::bind_rows(data,
                 prevYrWind)


# TESTING - issues with double hours
# (test<-importFeatherFcn(feather=dataPath,
#                        parameter = "WSPD_SCLR",
#                        station = "Abbotsford A Columbia Street",
#   year=2020)$stationData %>%
#     
#     dplyr::arrange(DATE_PST) %>%
#     
#     dplyr::filter(lubridate::year(DATE_PST)==yearToValidate)
#   ) 
# 
# test %>% last(.,n=10)
# 
# NAfillFcn(test )%>%
#   dplyr::arrange(DATE_PST)
```

Pad time series with NA's to complete the annual time series. Note this includes down to the STATION_NAME_FULL looping level. (updated in Mar 2020). Looping through STATION_NAME isn't sufficient because it can lead to duplicates (between, for example, Birchbank_Golf_Course and Birchbank_Golf_Course_60).



```{r allStations}
# all stations in yearToValidate
(allStations<-data %>%
   # filter for yearToValidate:
  dplyr::filter(format(DATE_PST,"%Y") %in% yearToValidate) %>%
          dplyr::pull(STATION_NAME) %>%
          unique %>%
          sort
)



```


```{r saveExternally}

# save imported and formatted data to 
feather::write_feather(data,
                       "unverifiedData_unpadded.feather")

# save list of stations:

# save allStsations as df
saveRDS(allStations,
        "allStations.rds")

# save allStations as character vector
readr::write_csv(data %>%
                   dplyr::select(STATION_NAME) %>%
                   distinct %>%
                   arrange(STATION_NAME),
                 "allStations.csv")
```


```{r dataPadded,eval=TRUE}
# fill gaps with NA:
source("../dataImport/functions/NAfillFcn.R")

# fill with NA's and save each station to preppedData foler
purrr::walk(allStations,
            
            function(x){
              
            stnData<-NAfillFcn(data %>%
              dplyr::filter(STATION_NAME==x))
            
            saveRDS(stnData,
                    file.path("./preppedData", 
                              stringr::str_c(x,".rds",collapse="")))
            
            })
```

