---
title: "2021 Kootenay Data Validation"
author: "Donna Haga"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)

# import rawData - only works for Donna
rawData<-feather::read_feather("C:\\HagaR\\AnnualDataValidation/unverifieddata_unpadded.feather")
```


## 2020 Wind Data in Teck Metals network 

WSPD_SCLR and WDIR_VECT is missing for all 4 stations (Birchbank Golf Course, Trail Butler Park, Trail Columbia Gardens Airport, and Warfield Elementary) in Teck Metals netowrk on the ftp:
`ftp://ftp.env.gov.bc.ca/pub/outgoing/AIR/AnnualSummary/2020/`

Note that Warfield Elementary wind data from 2014-09-01 to present has been invalidated, so all data populated in this folder shoudl be NA's.

```{r teckMetals2020wind}

data <- tibble::as_tibble(
  
  data.table::fread(
    "ftp://ftp.env.gov.bc.ca/pub/outgoing/AIR/AnnualSummary/2020/WSPD_SCLR.csv",
    header = TRUE,
    verbose = TRUE,
    showProgress = TRUE,
    fill = TRUE,
    colClasses = "character"
  ) %>%
  
  dplyr::bind_rows(
    
    data.table::fread(
     "ftp://ftp.env.gov.bc.ca/pub/outgoing/AIR/AnnualSummary/2020/WDIR_VECT.csv",
      header = TRUE,
      verbose = TRUE,
      showProgress = TRUE,
      fill = TRUE,
      colClasses = "character"
    )  
  )
    
  )

DT::datatable(data %>% 
                dplyr::distinct(STATION_NAME,PARAMETER) %>%
                dplyr::arrange(STATION_NAME),
              caption="Summary of wind data in 2020.",
              rownames=FALSE)
```
