---
title: "Annual Data Validation"
author: "Air Quality Section | Regional Operations Branch"
date: "`r format(Sys.time(), '%B %d, %Y')`"
params:
  preppedData: !r stringr::str_c("./preppedData/",dir('./preppedData')[97],collapse="")
  year: 2021
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    config:
      toc:
        collapse: section
---

```{r setup,echo=FALSE,warning=FALSE,message=FALSE}
# To do's for next year:
# - add range slider to plotly so it's easy to pan along axes:
 #(https://plotly.com/r/range-slider/)
# - round aqs stats to match ecms
# - add difference row to sas summary

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE)

library(tidyverse)
library(openair)
library(Hmisc)
library(xts)
library(plotly)
library(RCurl)
library(DT)
library(feather)
library(magrittr)
library(readxl)
library(gdata)

# functions to calculate SAS stats from hourly data
source("./SAS_from_ftpData/pm25sasFcn.R")
source("./SAS_from_ftpData/pm10sasFcn.R")
source("./SAS_from_ftpData/no2sasFcn.R")
source("./SAS_from_ftpData/nosasFcn.R")
source("./SAS_from_ftpData/so2sasFcn.R")
source("./SAS_from_ftpData/o3sasFcn.R")
source("./SAS_from_ftpData/h2ssasFcn.R")
source("./SAS_from_ftpData/trssasFcn.R")
source("./SAS_from_ftpData/cosasFcn.R")

# path to ecms sas reports saved locally:
sasReports<-"C:/HagaR/AnnualDataValidation/SAS_reports"

source("plotlyFcn.R")
source("emptyPlot.R")

```

```{r importData}
data<-readRDS(params$preppedData)

# data<-readRDS("./preppedData/Grand Forks City Hall.rds")

prevYrWind<-data %>%
  dplyr::filter(lubridate::year(DATE_PST)!=params$year &
                  PARAMETER %in% c("WSPD_SCLR","WDIR_VECT"))

data %<>%
  dplyr::filter(lubridate::year(DATE_PST)==params$year) %>%
  dplyr::group_by(PARAMETER) %>%
  dplyr::filter(!all(is.na(RAW_VALUE))) %>% dplyr::ungroup(.)
```


```{r dailyData}
day<-data %>%
    # rename to date for openair
    dplyr::rename(date=DATE_PST) %>%
    dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) %>%
    dplyr::group_modify(~ openair::timeAverage(.x,
                                               pollutant="RAW_VALUE",
                                               avg.time = "day",
                                               data.thresh = 75)
    ) %>%
    ungroup %>%
    dplyr::rename(DATE_PST=date)

`24hr`<-data %>%
    # rename to date for openair
    dplyr::rename(date=DATE_PST) %>%
    dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) %>%
    dplyr::group_modify(~ openair::rollingMean(.x,
                                               pollutant="RAW_VALUE",
                                               width = 24,
                                               align = "right",
                                               data.thresh = 75,
                                               new.name = "RAW_VALUE")
    ) %>%
    ungroup %>%
    dplyr::rename(DATE_PST=date)

```


```{r hourlyAndDaily}

# combine hourly and day data sets in one tidy tibble
allData<-data %>%
  dplyr::select(names(day)) %>%
  dplyr::mutate(TIME_AVG = "Hourly") %>%
  dplyr::bind_rows(.,
                   day %>%
                     dplyr::mutate(TIME_AVG = "Daily")) %>%
  dplyr::bind_rows(.,
                   `24hr` %>%
                     dplyr::mutate(TIME_AVG = "24-HR Running Ave"))


```


# Preamble {-}

**This report is for `r data %>% dplyr::pull(STATION_NAME) %>% unique %>% sort`**. 

<!--chapter:end:index.Rmd-->

# Data Summary

```{r dataSummary, cache=FALSE}

DT::datatable(data %>%
                dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) %>%
                dplyr::summarise(`# Valid Hours`=sum(!is.na(RAW_VALUE))),
              caption = "Summary of data selected for validation.",
              rownames = FALSE)
```

# Daily Data Completeness

75% data completeness threshold applied to each day (i.e. 18+ valid hours needed in a day for the day to be valid)


```{r dailyCapturePlot}
# myColors<-rev(RColorBrewer::brewer.pal(n=3,name="RdBu"))[c(1,3)]

ggplot2::ggplot(
  day %>%
    
    dplyr::mutate(`Validity` = dplyr::if_else(is.na(RAW_VALUE),
                                              "Invalid Days",
                                              "Valid Days")),
  aes(x = DATE_PST,
      y = PARAMETER,
      fill = Validity)
) +
  
  # ggplot2::facet_wrap(vars(PARAMETER)) +
  
  ggplot2::geom_tile(aes(color=`Validity`)) +
  
  scale_fill_manual(values=c("red","blue"),name="")+
  
  scale_color_manual(values=c("red","blue"),name="")+

  # scale_x_date(breaks=seq(lubridate::ymd("2020-01-01"),
  #                         lubridate::ymd("2021-12-31"),
  #                         by="1 month"),
  #              date_labels = "%b-%Y")+
  
  ggplot2::theme_bw() +
  
  theme(axis.text.x = element_text(angle = 90,vjust=0.5),
        legend.position = "top") +
  
  labs(title="Daily Data Capture",
       x="",
       y="")


```

<!--chapter:end:01-dataSummary.Rmd-->

# SAS Statistics {.tabset}

```{r sasOptions}
knitr::opts_chunk$set(cache = FALSE)

sasReports<-"./SAS_reports"
```

Note: all of the summaries below will have one fewer hour for the AQS sourced analysis. This is a bug, will try to resolve for next year.

## PM~2.5~

```{r pm25sas}

pm25sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% "PM25") %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% "PM25" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm25SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm25sas %<>% dplyr::mutate(ORIGIN="AQS")

```


```{r pm25sasECMS}
# get pm25 stations in data
pm25Stns<-data %>%
  dplyr::filter(PARAMETER=="PM25") %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(pm25Stns!=0)){

# import ecms sas from excel
pm25sasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "PM2.5_UNSUPPRESSED.xlsx")) %>%

# remove secondary header row
dplyr::slice(-1) %>%
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) %>%
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm25Stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm25sasECMS))
# utils::View(names(pm25sas))
# 
# tibble::tibble(names(pm25sasECMS),
#                names(pm25sas)) %>% utils::View(.)

pm25sasECMS %<>%
  dplyr::select(1:31,33,34,32,everything())

names(pm25sasECMS) <- names(pm25sas)

}
 
```

```{r pm25sasDT}
if(length(pm25Stns)!=0){

  if(exists("pm25sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm25sasDT <- bind_rows(
  pm25sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  pm25sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm25sasDT,
    caption = dplyr::if_else(nrow(pm25sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")} # this seems redundant - TO DO: TRY REMOVING IT AND SEE IF IT CRASHES
  }

# case 2: no data for this parameter
if(length(pm25Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## PM~10~
```{r pm10sas}

pm10sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% "PM10") %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% "PM10" &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   pm10SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
pm10sas %<>% dplyr::mutate(ORIGIN="AQS")

```


```{r pm10sasECMS}
# get pm10 stations in data
pm10Stns<-data %>%
  dplyr::filter(PARAMETER=="PM10") %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(pm10Stns!=0)){

# import ecms sas from excel
pm10sasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "PM10_UNSUPPRESSED.xlsx")) %>%

# remove secondary header row
dplyr::slice(-1) %>%
  
  # remove quarterly capture (duplicated)
  dplyr::select(-c(`EMS ID`,
                              `NAPS ID`,
                              REGION,
                              OWNER,
                              UNIT)) %>%
  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(pm10Stns, "_", " "))


# MATCH NAMES AND DATA STRUCTURE - ORDER OF DAILY EXCEEDANCES, 98P , 3-YR 98P IS MISMATCHED.

# utils::View(names(pm10sasECMS))
# utils::View(names(pm10sas))
# 
# tibble::tibble(names(pm10sasECMS),
#                names(pm10sas)) %>% utils::View(.)

pm10sasECMS %<>%
  dplyr::select(1:31,33,34,32,everything())

names(pm10sasECMS) <- names(pm10sas)

}
 
```

```{r pm10sasDT}
if(length(pm10Stns)!=0){

  if(exists("pm10sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

pm10sasDT <- bind_rows(
  pm10sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  pm10sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    pm10sasDT,
    caption = dplyr::if_else(nrow(pm10sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(pm10Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}

```

## NO~2~

```{r no2sas}

no2sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("no2")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("no2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   no2SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

# add column origin for where calculations originate from
no2sas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r no2sasECMS}
# get no2 stations in data
no2Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("no2")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(no2Stns)!=0){

# import ecms sas from excel
no2sasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "NO2_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded column
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(no2Stns, "_", " "))


# tibble::tibble(names(no2sasECMS),
#                names(no2sas)) %>% View

names(no2sasECMS) <- names(no2sas)

}
 
```

```{r no2sasDT}
if(length(no2Stns)!=0){

  if(exists("no2sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

no2sasDT <- bind_rows(
  no2sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  no2sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    no2sasDT,
    caption = dplyr::if_else(nrow(no2sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(no2Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## NO

```{r nosas}

nosas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("no")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("no") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   noSASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
nosas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r nosasECMS}
# get no stations in data
noStns<-data %>%
  dplyr::filter(PARAMETER==toupper("no")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(noStns)!=0){

# import ecms sas from excel
nosasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "NO_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(noStns, "_", " "))


# tibble::tibble(names(nosasECMS),
#                names(nosas)) %>% View

names(nosasECMS) <- names(nosas)

}
 
```

```{r nosasDT}
if(length(noStns)!=0){

  if(exists("nosasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

nosasDT <- bind_rows(
  nosasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  nosas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    nosasDT,
    caption = dplyr::if_else(nrow(nosasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(noStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## SO~2~

```{r so2sas}

so2sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("so2")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("so2") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   so2SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

    # add column origin for where calculations originate from
so2sas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r so2sasECMS}
# get so2 stations in data
so2Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("so2")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(so2Stns)!=0){

# import ecms sas from excel
so2sasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "SO2_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(so2Stns, "_", " "))


# tibble::tibble(names(so2sasECMS),
#                names(so2sas)) %>% View

names(so2sasECMS) <- names(so2sas)
 
}
```

```{r so2sasDT}
if(length(so2Stns)!=0){

  if(exists("so2sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

so2sasDT <- bind_rows(
  so2sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  so2sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    so2sasDT,
    caption = dplyr::if_else(nrow(so2sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(so2Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## O~3~

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQS calculations, these 7 hours were not included which leads to small differences with the ECMS calculations.

```{r o3sas}

o3sas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("o3")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("o3") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   o3SASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

 # add column origin for where calculations originate from
o3sas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r o3sasECMS}
# get o3 stations in data
o3Stns<-data %>%
  dplyr::filter(PARAMETER==toupper("o3")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(o3Stns!=0)){

# import ecms sas from excel
o3sasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "OZONE_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(o3Stns, "_", " "))


# tibble::tibble(names(o3sasECMS),
#                names(o3sas)) %>% View

names(o3sasECMS) <- names(o3sas)

}
 
```

```{r o3sasDT}
if(length(o3Stns)!=0){

  if(exists("o3sasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

o3sasDT <- bind_rows(
  o3sasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  o3sas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    o3sasDT,
    caption = dplyr::if_else(nrow(o3sasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(o3Stns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


## H~2~S

```{r h2ssas}

h2ssas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("h2s") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   h2sSASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  # add column origin for where calculations originate from
h2ssas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r h2ssasECMS}
# get h2s stations in data
h2sStns<-data %>%
  dplyr::filter(PARAMETER==toupper("h2s")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(h2sStns)!=0){
# import ecms sas from excel
h2ssasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "H2S_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(h2sStns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(h2ssasECMS),
#                names(h2ssas)) %>% View

# utils::View(names(h2ssasECMS))

# got to here
names(h2ssasECMS) <- names(h2ssas)

} 
 
```

```{r h2ssasDT}
if(length(h2sStns)!=0){

  if(exists("h2ssasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

h2ssasDT <- bind_rows(
  h2ssasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  h2ssas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    h2ssasDT,
    caption = dplyr::if_else(nrow(h2ssasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(h2sStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## TRS

```{r trssas}

trssas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("trs")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("trs") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   trsSASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

   # add column origin for where calculations originate from
trssas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r trssasECMS}
# get trs stations in data
trsStns<-data %>%
  dplyr::filter(PARAMETER==toupper("trs")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(trsStns!=0)){

# import ecms sas from excel
trssasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "TRS_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(trsStns, "_", " "))

# CHECK THE COLUMNS MATCH
# tibble::tibble(names(trssasECMS),
#                names(trssas)) %>% View

names(trssasECMS) <- names(trssas)

}
 
```

```{r trssasDT}
if(length(trsStns)!=0){

  if(exists("trssasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

trssasDT <- bind_rows(
  trssasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  trssas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    trssasDT,
    caption = dplyr::if_else(nrow(trssasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(trsStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```

## CO

Some of these statistics are based on 8-hour rolling averages, requiring the last 7 hours of the previous year. For the AQS calculations, these 7 hours were not included which leads to small differences with the ECMS calculations.

```{r cosas}

cosas<-purrr::map_dfr((data %>%
                dplyr::filter(PARAMETER %in% toupper("co")) %>%
                dplyr::distinct(STATION_NAME) %>%
                arrange(STATION_NAME))$STATION_NAME,

             function(station){

               station<-data %>%
                 dplyr::filter(PARAMETER %in% toupper("co") &
                                 STATION_NAME %in% station)

               purrr::map_dfr(unique(station$INSTRUMENT),

                 function(instrument){

                   instrument<-station %>%
                     dplyr::filter(INSTRUMENT %in% instrument)

                   coSASFcn(data=instrument)

                 }) #INSTRUMENT LOOP

             }) #STATION LOOP

  
# add column origin for where calculations originate from
cosas %<>% dplyr::mutate(ORIGIN="AQS")

```

```{r cosasECMS}
# get co stations in data
coStns<-data %>%
  dplyr::filter(PARAMETER==toupper("co")) %>%
  dplyr::pull(STATION_NAME) %>%
  unique

if(length(coStns)!=0){

# import ecms sas from excel
cosasECMS <- readxl::read_excel(
  file.path(sasReports,                                            
            "CO_UNSUPPRESSED.xlsx")) %>%
  
  # remove unneeded columna
  dplyr::select(-c(`EMS ID`,                    
                   `NAPS ID`,
                   REGION,
                   OWNER,
                   UNIT)) %>% 

# remove secondary header row
dplyr::slice(-1) %>%

  # FOR SUMMARY TABLE
  dplyr::mutate(ORIGIN = "ECMS") %>%
  # FILTER FOR YEAR AND STATIONS
  dplyr::filter(YEAR == params$year &
                  `STATION NAME` %in% stringr::str_replace(coStns, "_", " "))


# tibble::tibble(names(cosasECMS),
#                names(cosas)) %>% View

names(cosasECMS) <- names(cosas)

}
 
```

```{r cosasDT}
if(length(coStns)!=0){

  if(exists("cosasECMS")){
   
    # issues with binding, mismatching column formats (character vs integer), not being able to convert from one form to the other. Convert everything to character for data table.

cosasDT <- bind_rows(
  cosasECMS %>%
    dplyr::mutate_all(as.character) %>%
    dplyr::mutate(`STATION NAME` = toupper(`STATION NAME`)),

  cosas %>%
    mutate_all(as.character)

) %>%
  dplyr::arrange(`STATION NAME`) %>%
  dplyr::select(ORIGIN, everything())


   DT::datatable(
    cosasDT,
    caption = dplyr::if_else(nrow(cosasECMS)!=0,
                             "ECMS and AQS calculated statistics.There will be one fewer valid hour compared to ECMS stats, I'll try to resolve this for next year.",
                             "AQS calculated statistics. (No summary available from ECMS.)"),
    options = list(
      scrollX = TRUE,
      scroller = TRUE,
      scrollY = 300,
      searching = TRUE,
      paging = TRUE,
      pageLength = 25
    )
  )
   
   
  }else{htmltools::tags$p("No SAS summary for this parameter.")}
  }

# case 2: no data for this parameter
if(length(coStns)==0) {
  htmltools::tags$p("There is no data for this parameter.")
}
```


<!--chapter:end:02-sas.Rmd-->

# Time series {.tabset}

```{r hourlyPlotOptions}
knitr::opts_chunk$set(cache = FALSE)
```

## PM~2.5~

```{r pm25hourly}
pm25plots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("pm25") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
 plotlyFcn(data,
          allData,
          parameter=toupper("pm25"))
  
  
}

htmltools::tagList(pm25plots)
```


## PM~10~

```{r pm10hourly}
pm10plots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("pm10") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
            allData,
            parameter=toupper("pm10"))
  
  
}

htmltools::tagList(pm10plots)
```

## O~3~

```{r o3hourly}
o3plots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("o3") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("o3"))
  
  
}

htmltools::tagList(o3plots)
```

## NO~2~

```{r no2hourly}
no2plots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("no2") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,    
            allData,

            parameter=toupper("no2"))
  
  
}

htmltools::tagList(no2plots)
```

## NO

```{r nohourly}
noplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("no") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("no"))
  
  
}

htmltools::tagList(noplots)
```

## NO~x~

```{r noxhourly}
noxplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% "NOx" & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter="NOx")
  
  
}

htmltools::tagList(noxplots)
```


## SO~2~

```{r so2hourly}
so2plots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("so2") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("so2"))
  
  
}

htmltools::tagList(so2plots)
```

## CO

```{r cohourly}
coplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("co") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("co"))
  
  
}

htmltools::tagList(coplots)
```

## TRS

```{r trshourly}
trsplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("trs") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("trs"))
  
  
}

htmltools::tagList(trsplots)
```

## H~2~S

```{r h2shourly}
h2splots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("h2s") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("h2s"))
  
  
}

htmltools::tagList(h2splots)
```

## WS

Something to look for: ws/wd lock due to rime on the anemometer or vane, data coming online after long periods (multiple hours) of being offline only to have the first hour read high, then all subsequent hours much lower.

```{r wspd_sclrhourly}
wspd_sclrplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("wspd_sclr") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("wspd_sclr"))
  
  
}

htmltools::tagList(wspd_sclrplots)
```

## WD

Something to look for: ws/wd lock due to rime on the anemometer or vane, data coming online after long periods (multiple hours) of being offline only to have the first hour read high, then all subsequent hours much lower.

```{r wdir_vecthourly}
wdir_vectplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("wdir_vect")& !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("wdir_vect"))
  
  
}

htmltools::tagList(wdir_vectplots)
```

## Temp

```{r temp_meanhourly}
temp_meanplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("temp_mean") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("temp_mean"))
  
  
}

htmltools::tagList(temp_meanplots)
```

## Humidity

```{r humidityhourly}
humidityplots<-if(
  
  (data %>% 
       dplyr::filter(PARAMETER %in% toupper("humidity") & !is.na(RAW_VALUE)) %>%
       nrow(.))==0
  
) {htmltools::tags$p("There is no data for this parameter.")} else {
  
  plotlyFcn(data,
                        allData,

            parameter=toupper("humidity"))
  
  
}

htmltools::tagList(humidityplots)
```

<!--chapter:end:03-timeSeries.Rmd-->

# Box Plots {.tabset}

```{r boxPlotOptions}
knitr::opts_chunk$set(cache = FALSE)

station<-data %>%
             dplyr::pull(STATION_NAME) %>%
             unique
```

```{r dataPrep}
# add units becuase it is used below and in the plots

# look at all the unique paramters
# data %>% dplyr::distinct(PARAMETER)

data %<>%
  mutate(UNIT=dplyr::case_when(
    
    PARAMETER %in% c("CO",
                     "NO",
                     "NO2",
                     "NOx",
                     "O3",
                     "SO2",
                     "H2S",
                     "TRS") ~ "ppb",
    
    PARAMETER %in% c("PM10",
                     "PM25") ~ "ug/m3",
    
    PARAMETER == "HUMIDITY" ~ "%",
    
    PARAMETER == "TEMP_MEAN" ~ "deg. C",
    
    PARAMETER == "WDIR_VECT" ~ "deg.",
    
    PARAMETER == "WSPD_SCLR" ~ "m/s"
    
    
    
    
  ))


```


## PM~2.5~

```{r pm25Data}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm25"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no PM2.5 data at this station.")}

```


```{r pm25monthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    

    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm25"))
    
    if(nrow(plotData)!= nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
       ){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly PM2.5 (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("pm25")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    } 
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r pm25hebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm25"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly PM2.5 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("pm25")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r pm25diurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm25"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly PM2.5 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("pm25")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## PM~10~

```{r pm10Data}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm10"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no PM10 data at this station.")}

```

```{r pm10monthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    
    #FOR TESTING - 9 total
# (station<-(data %>%
#              dplyr::filter(PARAMETER %in% toupper("pm10")) %>%
#              dplyr::pull(STATION_NAME) %>%
#              unique)[4])
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm10"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly PM10 (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("pm10")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r pm10hebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm10"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly pm10 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("pm10")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r pm10diurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm10"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly pm10 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("pm10")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```


## O~3~


```{r o3Data}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("o3"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no O3 data at this station.")}

```

```{r o3monthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    
    #FOR TESTING - 9 total
# (station<-(data %>%
#              dplyr::filter(PARAMETER %in% toupper("o3")) %>%
#              dplyr::pull(STATION_NAME) %>%
#              unique)[4])
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("o3"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly o3 (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("o3")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }  
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r o3hebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("o3"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly o3 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("o3")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r o3diurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("o3"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly o3 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("o3")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## NO~2~

```{r no2Data}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no2"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no NO2 data at this station.")}

```

```{r no2monthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    
    #FOR TESTING - 9 total
# (station<-(data %>%
#              dplyr::filter(PARAMETER %in% toupper("no2")) %>%
#              dplyr::pull(STATION_NAME) %>%
#              unique)[4])
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no2"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly no2 (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("no2")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }  
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r no2hebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no2"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly no2 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("no2")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r no2diurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no2"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly no2 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("no2")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## NO

```{r noData}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no NO data at this station.")}

```

```{r nomonthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    
    #FOR TESTING - 9 total
# (station<-(data %>%
#              dplyr::filter(PARAMETER %in% toupper("no")) %>%
#              dplyr::pull(STATION_NAME) %>%
#              unique)[4])
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly no (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("no")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
    plotly::ggplotly(p) 
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r nohebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly no (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("no")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r nodiurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly no (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("no")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## NO~x~

```{r noxData}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% "NOx")

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no NOx data at this station.")}

```

```{r noxmonthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    
    #FOR TESTING - 9 total
# (station<-(data %>%
#              dplyr::filter(PARAMETER %in% "NOx") %>%
#              dplyr::pull(STATION_NAME) %>%
#              unique)[4])
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% "NOx")
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly nox (",
                              data %>%
                                dplyr::filter(PARAMETER %in% "NOx") %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    } 
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r noxhebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% "NOx")%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly nox (",
          data %>%
            dplyr::filter(PARAMETER %in% "NOx") %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r noxdiurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% "NOx")
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly nox (",
          data %>%
            dplyr::filter(PARAMETER %in% "NOx") %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## SO~2~

```{r so2Data}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("so2"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no SO2 data at this station.")}

```

```{r so2monthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    

    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("so2"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly so2 (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("so2")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }  
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r so2hebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("so2"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly so2 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("so2")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r so2diurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("so2"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly so2 (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("so2")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## CO

```{r coData}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("co"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no CO data at this station.")}

```

```{r comonthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    

    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("co"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly co (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("co")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }  
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r cohebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("co"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly co (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("co")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r codiurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("co"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly co (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("co")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## TRS

```{r trsData}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("trs"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no TRS data at this station.")}

```


```{r trsmonthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    

    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("trs"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly trs (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("trs")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }  
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r trshebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("trs"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly trs (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("trs")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    }
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r trsdiurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("trs"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly trs (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("trs")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## H~2~S

```{r h2sData}

plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("h2s"))

if(nrow(plotData)== nrow(plotData %>%
                             dplyr::filter(is.na(RAW_VALUE)))
){htmltools::tags$p("There is no H2S data at this station.")}

```

```{r h2smonthly}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
    
  
    {
    
    #FOR TESTING - 9 total
# (station<-(data %>%
#              dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
#              dplyr::pull(STATION_NAME) %>%
#              unique)[4])
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("h2s"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
           aes(x = reorder(format(DATE_PST, "%b"), DATE_PST), #alter this for different boxplots
               y = RAW_VALUE,
               fill=STATION_NAME)
           ) +
      geom_boxplot() +
      labs(title = paste("Monthly Boxplot:",
                         station),
           x = "",
           y = stringr::str_c("Hourly h2s (",
                              data %>%
                                dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
                                dplyr::pull(UNIT) %>% unique, ")",
                              sep = ""
             )
           ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      )+ 
        scale_fill_brewer(palette = "Set1")+
      facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  # Error in fix.by(by.y, y) : 'by' must specify uniquely valid columns
    plotly::ggplotly(p) 
    
    }  
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

```{r h2shebdomadal}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("h2s"))%>%
        dplyr::mutate(weekday=factor(format(DATE_PST,"%a"),
                                     c("Sun",
                                        "Mon",
                                        "Tue",
                                        "Wed",
                                        "Thu",
                                        "Fri",
                                        "Sat")))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData ,
      aes(
        x = weekday,
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Hebdomadal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly h2s (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
      
    } #end plot function
  
  )# end map
  
) #end tagList

) # end suppressWarnings

```

```{r h2sdiurnal}
suppressWarnings(
  
  htmltools::tagList(
  
  purrr::map(station,
  
  function(station)
  # station<-"Abbotsford A Columbia Street"
    {
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("h2s"))
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(
      data = plotData,
      aes(
        x = format(DATE_PST,"%H"),
        #alter this for different boxplots
        y = RAW_VALUE,
        fill = STATION_NAME
      )
    ) +
      geom_boxplot() +
      scale_x_discrete()+
      labs(
        title = paste("Diurnal Boxplot:",station),
        x = "",
        y = stringr::str_c(
          "Hourly h2s (",
          data %>%
            dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
            dplyr::pull(UNIT) %>% unique,
          ")",
          sep = ""
        )
      ) +
      theme_bw() +
      theme(
        # axis.text.x = element_text(
        #   # angle = 60,
        #   vjust = 1,
        #   hjust = 1
        # ),
        legend.position = "none",
        legend.title = element_blank()
      ) +
      scale_fill_brewer(palette = "Set1") +
      facet_wrap(~ INSTRUMENT, scales = "free")
    
    plotly::ggplotly(p)
    
    } 
    
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

<!--chapter:end:04-boxPlots.Rmd-->

# Histograms {.tabset}


```{r histogramOptions}
knitr::opts_chunk$set(cache = FALSE)
```

## PM~2.5~

```{r pm25histogram}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("pm25"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p<-ggplot(data = plotData,
       aes(x = RAW_VALUE,
           fill = INSTRUMENT,
           color = INSTRUMENT)) +
  
  geom_histogram(alpha = 0.25,
                 binwidth = 1) +
  
  labs(
    title = paste("Histogram:",
                  station),
    y = "Count",
    x = stringr::str_c(
      "Hourly PM2.5 (",
      data %>%
        dplyr::filter(PARAMETER %in% toupper("pm25")) %>%
        dplyr::pull(UNIT) %>% unique,
      ")",
      sep = ""
    )
  ) +
  theme_bw() +
  theme(legend.position = "none",
        legend.title = element_blank()) +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap( ~ INSTRUMENT, scales = "free") 
    
  plotly::ggplotly(p) 
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```


## PM~10~

```{r pm10histogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
    
    plotData <- data %>%
      dplyr::filter(STATION_NAME %in% station &
                      PARAMETER %in% toupper("pm10"))
    
    if (nrow(plotData) != plotData %>%
        dplyr::summarise(nas = sum(is.na(RAW_VALUE))) %>%
        dplyr::pull(nas)) {
      
      p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly PM10 (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("pm10")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p) 
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```


## O~3~

```{r o3histogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {

    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("o3"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    
      p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly O3 (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("o3")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```


## NO~2~

```{r no2histogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
    
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no2"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly NO2 (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("no2")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p) 
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## NO

```{r nohistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {

    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("no"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly NO (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("no")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p) 
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## NO~x~

```{r noxhistogram}
suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
  
    {

    plotData <- data %>%
      dplyr::filter(STATION_NAME %in% station &
                      PARAMETER %in% "NOx")
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly NOx (",
            data %>%
              dplyr::filter(PARAMETER %in% "NOx") %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## SO~2~

```{r so2histogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("so2"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly SO2 (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("so2")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## CO

```{r cohistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {

    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("co"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
     p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly CO (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("co")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## TRS


```{r trshistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
    
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("trs"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly TRS (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("trs")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## H~2~S

```{r h2shistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("h2s"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly H2S (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("h2s")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings

```

## Wind Speed (Scalar)

```{r wshistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("wspd_sclr"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly Wind Speed (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("wspd_sclr")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings
```

## Wind Direction (Vector)

```{r wdhistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("wdir_vect"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly Wind Direction (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("wdir_vect")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings
```

## Humidity

```{r humidityhistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("humidity"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly Humidity (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("humidity")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings
```

## Temperature

```{r temphistogram}

suppressWarnings(
  htmltools::tagList(
  
  purrr::map(data %>%
             dplyr::pull(STATION_NAME) %>%
             unique,
  
  function(station)
    
  
    {
   
    plotData<-data %>% 
             dplyr::filter(STATION_NAME %in% station &
                             PARAMETER %in% toupper("temp_mean"))
    
    if(nrow(plotData)!=plotData %>% 
      dplyr::summarise(nas=sum(is.na(RAW_VALUE))) %>%
      dplyr::pull(nas)){
    
    p <- ggplot(data = plotData,
                  aes(x = RAW_VALUE,
                      fill = INSTRUMENT,
                      color = INSTRUMENT)) +
        
        geom_histogram(alpha = 0.25,
                       binwidth = 1) +
        
        labs(
          title = paste("Histogram:",
                        station),
          y = "Count",
          x = stringr::str_c(
            "Hourly Temperature (",
            data %>%
              dplyr::filter(PARAMETER %in% toupper("temp_mean")) %>%
              dplyr::pull(UNIT) %>% unique,
            ")",
            sep = ""
          )
        ) +
        theme_bw() +
        theme(legend.position = "none",
              legend.title = element_blank()) +
        scale_fill_brewer(palette = "Set1") +
        facet_wrap(~ INSTRUMENT, scales = "free")
      
      plotly::ggplotly(p)  
    
    }  else{htmltools::tags$p("There is no data for this parameter.")}#end if and else
      
    } #end plot function
  
  )# end map
  
) #end tagList

) #end suppressWarnings
```

<!--chapter:end:05-histograms.Rmd-->

# Wind Roses

Wind roses for `r params$year` and 5 previous years (when available). 

Things to look for when validating wind data:

+ Annual windrose
+ Windrose from previous years
+ Percent calm winds for the past 5-8 years
+ Do we have any pictures of the station?
+ Does the windrose make sense to you relative to the local topography?
+ RH - does RH get to 100% or does it max out at 97%? Has this changed recently?
+ Can I see any obvious breakpoints in a strip chart where something changes/

```{r windCache}
knitr::opts_chunk$set(cache = FALSE)
```


```{r windDataPrepQAQC}
# select wind data, get it in openair format

windData <- data %>% # data from importData chunk in index.Rmd
  
  dplyr::filter(PARAMETER %in% c("WSPD_SCLR", "WDIR_VECT")) %>%
  
  # contains X previous years as per _01.importData.html 
  dplyr::bind_rows(.,
                   prevYrWind) %>%
  
  # 2021 VALIDATION BUGS
  
  # # # COLWOOD CITY HALL 
  # duplicates in wspd_sclr,wdir_vect from 2020-01-01 03:00:00 to 2020-09-01 13:00:00 (one NA, one value)
  
  
  # # # PRINCE GEORGE EXPLORATION PLACE
  # duplicates in wspd_sclr,wdir_vect and humidity from 2021-01-01 01:00:00 until 2021-12-31 23:00:00
  
  # # # VANDERHOOF COURTHOUSE
  # duplicates in wspd_sclr,wdir_vect 2021-01-01 01:00:00 until 2021-12-31 23:00:00
  
  
  
  # # # 
  # duncan college street has duplicates for unique DATE_PST,STATION_NAME,PARAMETER
  # (no duplicates when grouped by STATION_NAME and STATION_NAME_FULL because _60 has
  # the duplicates i.e. UNSPECIFIED for instrument and "" for all the data). Filter out this data.
  # communicated to ecms
  
  dplyr::filter(!(STATION_NAME=="Duncan College Street" & INSTRUMENT == "UNSPECIFIED")) %>%
  
  # # # 
  # burns lake sheraton east - duplicates in wind data (one is prob from _60 but should still get cleaned up). 
  # NOT communicated to ecms
  
  dplyr::filter(!(STATION_NAME=="Burns Lake Sheraton East" & 
                    INSTRUMENT == "WIND DIR VECTOR" &
                    lubridate::year(DATE_PST)==2016)) %>%

  # # # 
  # courtenay elementary school - duplicates from 2017-01-01 until 2019-12-31 where instrument=WIND DIR VECTOR are all NA's and INSTRUMENT=WIND DIR have values


  # remove wind direction duplicates (all NA values)
  dplyr::filter(!(STATION_NAME=="Courtenay Elementary School" &
                  INSTRUMENT=="WIND DIR VECTOR" &
                  lubridate::year(DATE_PST) %in% 2017:2019))  %>%

  # # # FRASER LAKE ENDAKO MINES
  dplyr::filter(!(STATION_NAME=="Fraser Lake Endako Mines" &
                  INSTRUMENT=="UNSPECIFIED" &
                  lubridate::year(DATE_PST)==2016)) %>%

  # # # TAYLOR SOUTH HILL
  # nuanced duplicates in wspd_sclr and wdir_vect for all of 2020. 
  # For jan 1, 2020 00:00:00 INSTRUMENT %in% c("WIND DIR VECTOR", "WIND SPEED") need to removed
  # for the rest of the year INSTRUMENT == "UNSPECIFIED" needs to be removed
  dplyr::filter(!(STATION_NAME=="Taylor South Hill" &
                  INSTRUMENT %in% c("WIND DIR VECTOR",
                                    "WIND SPEED") &
                  DATE_PST==lubridate::ymd_hms("2020-01-01 00:00::00",
                                               tz="Etc/GMT+8"))) %>%
  
  dplyr::filter(!(STATION_NAME=="Taylor South Hill" &
                  INSTRUMENT == "UNSPECIFIED" &
                  DATE_PST %in% seq(lubridate::ymd_hms("2020-01-01 01:00::00",
                                               tz="Etc/GMT+8"),
                                    lubridate::ymd_hms("2020-12-31 23:00::00",
                                               tz="Etc/GMT+8"),
                                    by="hour"
                                    )))

  
# # # COURTENAY ELEMENTARY SCHOOL WIND SPEED
# couldn't figure out how to add this to the pipe above (ideal option)
  # wind speed has duplicates with double hours with two numeric values (one is zero and on is the real value) between 2017-05-29 20:00:00 and 2017-06-01 00:00:00 (inclusive) - THIS WILL NEED TO BE REMOVED ONCE FIXED ON THE FTP OTHERWISE IT'S GOING TO DELETE REAL DATA

# if(
#   
#   stringr::str_detect(params$preppedData,
#                       "Courtenay Elementary School")
# ){windData<-
#   
#   dplyr::anti_join(
#     windData,
#     #isolate even rows to remove
#     windData %>%
#       dplyr::filter(
#         STATION_NAME == "Courtenay Elementary School",
#         PARAMETER == "WSPD_SCLR" &
#           DATE_PST %in% seq(
#             lubridate::ymd_hms("2017-05-29 20:00:00",
#                                tz = "Etc/GMT+8"),
#             lubridate::ymd_hms("2017-06-01 00:00:00",
#                                tz = "Etc/GMT+8"),
#             by = "hour"
#           )
#       ) %>%
#       # even rows - shoudl be all zeros
#       dplyr::slice(seq(2,nrow(.),2))
#       )}
# 
# ## # # FIND DUPLICATES
#  duplicates<-windData %>%
#     dplyr::group_by(DATE_PST, STATION_NAME, PARAMETER) %>%
#     dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
#     dplyr::filter(n > 1L) %>%
#    dplyr::left_join(.,
#                     windData,
#                     by=c("DATE_PST","STATION_NAME","PARAMETER"))
# 
#  write.csv(duplicates,"duplicates.csv")
# 
#  duplicates %>%
#    dplyr::group_by(PARAMETER) %>%
#    dplyr::slice(1:6) %>% utils::View()
# 
#   # are any groups all NA's? makes it easy to remove
#  duplicates %>%
#    # dplyr::filter(PARAMETER=="WSPD_SCLR") %>%
#    dplyr::group_by(PARAMETER,INSTRUMENT) %>%
#    dplyr::summarise(`# NA's`=sum(is.na(RAW_VALUE)),
#                     `# Obs`=sum(!is.na(RAW_VALUE)),
#                     `# Hours`=dplyr::n())
# 
# 
# 
# duplicates %>%
#   dplyr::group_by(STATION_NAME,PARAMETER,INSTRUMENT) %>%
#   dplyr::summarise(start=min(DATE_PST),
#                    end=max(DATE_PST))


 
 # # # END DUPLICATES
  
```

```{r windDataOpenAir}
if( all(nrow(windData)!=0, # at least one row of data
        any(unique(windData$PARAMETER) %in% "WSPD_SCLR"),
        any(unique(windData$PARAMETER) %in% "WDIR_VECT")
    )
  ){
  
 
  windData %<>%
    
    dplyr::select(date = DATE_PST,
                  STATION_NAME,
                  # INSTRUMENT,
                  PARAMETER,
                  RAW_VALUE) %>%
    
    tidyr::pivot_wider(.,
                       names_from = PARAMETER,
                       values_from = RAW_VALUE) %>%
    
    dplyr::rename(ws = WSPD_SCLR,
                  wd = WDIR_VECT) %>%
    
    dplyr::mutate(ws = ifelse(is.na(wd), NA_real_, ws),
                  wd = ifelse(is.na(ws), NA_real_, wd))
}

  

```

```{r windRose}
if(all(
  # at least a row of data
  nrow(windData) != 0, 
  # some data in the year being validated
  length(unique(lubridate::year(windData$date)) %in% params$year)!=0,
  # a column called ws
  any(names(windData) %in% "ws"),
  # a column called wd
  any(names(windData) %in% "wd")
         
       )
) {
  

purrr::walk(unique(lubridate::year(windData$date)) %>% sort,
    
    function(year){
      
      # TESTING
      
      # year<-2020
      # 
      # windDataBackup<-windData
      # 
      # windData<-windDataBackup
      
      # END TESTING
      
      station<-unique(windData$STATION_NAME)
      
      windData %<>%
        dplyr::filter(lubridate::year(date) %in% year)
      
      #number of calm hours
      ncalm <- windData %>%
        dplyr::filter(ws < 0.5) %>%
        dplyr::summarise(calms = n())
      
      #total number of valid ws hours
      ntotal <- windData %>%
        dplyr::filter(!is.na(ws)) %>%
        dplyr::summarise(total = n())
      
      #percentage calm (ws<0.5 m/s)
      pcalm <- round(100 * ncalm / ntotal,
                     digits = 2)
      
      #filter out calm windData
      roseData <- windData %>%
        dplyr::filter(ws >= 0.5)
      
      if(nrow(windData)==sum(is.na(windData$ws)) | nrow(roseData)==0){
        
        paste("There is either no paired wind data at",
              station,
              "or there is no paired wind data above the 0.5 m/s threshold.")
        
      } else {
      
      
      
      #windRose
      windRose(
        roseData,
        annotate = FALSE,
        breaks = c(0.5, 1.5, 3.3, 5.5, 7.9, 10.7, 13.8, 17.1),
        #Beaufort scale with 0.5 as lowest cut point.
        sub = paste("Calms (=<0.5m/s)=", pcalm, "%"),
        key.position = "right",
        main = stringr::str_c(year," Wind Rose at ",station),
        angle = 360 / 16,
        #16 spokes
        cols = "jet",
        paddle = FALSE
      ) 
      
      } # end else
      
    } #end function(station)
    
    ) # map
  
} else{
  
  htmltools::tags$p("This station either doesn't measure wind, has no wind data for the year being validated, or it is missing one of WSPD_SCLR or WDIR_VECT")
  
}


```

<!--chapter:end:06-windRoses.Rmd-->

# Minute Plots

For next year: minute data plotted above a year of hourly data  that is two separate figures plotted one above the other with negative values in a different colour

<!--chapter:end:07-minuteData.Rmd-->

# SHARP drift

For next year: 3 channel SHARP 5030 neph drift is important to identify

<!--chapter:end:08-sharpDrift.Rmd-->

